
\section{Conference presentations and invited seminars}
\denseouterlist{

\entry{ \textbf{2026:} IAE - CSIC Barcelona}

\entry{ \textbf{2025:} Catalan Economic Society, CUNEF Internal Workshop, EUI Alumni Conference. 48th Simposio of the Spanish Economic Association. }

\entry{ \textbf{2024:} Society for Institutional \& Organizational Economics (University of Chicago, Chicago). European Winter  Meeting of the Econometric Society . }

\entry{ \textbf{2023:} European Political Science Association Conference, Catalan Economic Society, Universidad Complutense de Madrid, CEMIR conference on International Migration (CESIFO, Munich), 48th Simposio of the Spanish Economic Association. }

\entry{ \textbf{2022:} Royal Holloway and Queen Mary Workshop on the Political Economy of Conflict.  47th Simposio of the Spanish Economic Association. }

\entry{ \textbf{2021:} Trento Workshop on Information Economics; European Political Science Association Conference 2021; Conference on Economic Studies;  European Economic Association Conference; American Political Science Association Conference 2021.}

\entry{ \textbf{2020:} Formal Theory Virtual Workshop.}

\entry{  \textbf{2019:} Spring Meeting of Young Economists; X Workshop on Institutions, Individual Behavior and Economic Outcomes; Annual Society for the Advancement of Economic Theory (SAET) Conference; 46th Annual Conference of the European Association for Research in Industrial Economics.}

\entry{ \textbf{2018:} 	17th session of the Institutional and Organizational Economics Academy (CNRS); 43rd Simposio of the Spanish Economic Association.}

\entry{ \textbf{2017:} 	CER-ETH, Zurich; Max Planck Institute for Tax Law and Public Finance; CUNEF; NICEP 2017; Annual Meeting of the Association of Southern European Economic Theorists; 42nd Simposio of the Spanish Economic Association.}

\entry{ \textbf{2016:} 	University of Leicester PhD Conference in Economics; Annual Meeting of the Association of Southern European Economic Theorists; Applied Economics Workshop (Petralia); Warwick PhD Conference; EUI Microeconomics Working Group.}
}

